Supporting Information for: \\ Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-27 paper/arxiv-submission/main_5_methods.tex
copy for cleanup: arxiv submit

\subsection{Catalyst models}
Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates,
including graphitic carbon nitride (g-C\textsubscript{3}N\textsubscript{4}), nitrogen-doped graphene,
graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C\textsubscript{2}N.
The specific single metal atoms studied are outlined in Supplementary \cref{supp_fig1:ptable}.
To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 \text{\AA} were introduced.

>>>>

\subsection{Catalyst models}
Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates,
including g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C\textsubscript{2}N.
The specific single metal atoms studied are outlined in Supplementary \cref{supp_fig1:ptable}.
To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 \text{\AA} were introduced.
